\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvstyle{classic} % Style options: 'casual', 'classic', 'banking', 'oldstyle', 'fancy'
\moderncvcolor{blue}   % Color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'

% character encoding
\usepackage[utf8]{inputenc}  


% adjust the page margins
\usepackage[scale=0.8]{geometry}

% personal data
\name{Grégoire}{Marabout-Demazure}
\title{Experienced Software Architect \\ Cloud, Data, \& AI Solutions}
\address{10 rue George Sand}{34920 le Crès}
\phone[mobile]{+33~6~60~65~64~61}
\email{gmarabout@gmail.com}
\homepage{www.liberscale.tech}
\social[linkedin]{gmarabout}
\social[github]{gmarabout}

\begin{document}
\makecvtitle

\section{Summary}
Cloud \& AI Architect with 20+ years of experience designing and scaling high-performance distributed systems. Expert in AI-driven automation, large-scale data pipelines, and cybersecurity solutions, helping businesses turn complex technical challenges into scalable, cloud-native solutions. Proven ability to lead engineering teams, drive innovation, and build AI-powered platforms that optimize operations and enhance security.

\section{Education}
\cventry{1996--1998}{B.S. in Computer Science and AI}{Université Pierre et Marie Curie}{Paris}{}{Artificial Intelligence, Mathematics}
\cventry{1994--1996}{Associate degree in Physics}{Université Pierre et Marie Curie}{Paris}{}{Energy, Quantum Physics, and Mechanics}




\section{Experience}

\cventry{2023--now}{Founder \& Cloud/AI Architect}{Liberscale}{Montpellier}{}{
	\begin{itemize}
		\item Designed and implemented a secure, cloud-native data pipeline for credential leak detection, improving threat intelligence and cybersecurity response.
		\item Developed an AI-powered SaaS automation platform with Hexa, leveraging large language models to automate and optimize enterprise workflows.
		\item Architected \href{https://taipy.io/}{Taipy}’s distributed execution mode, enabling scalable AI-driven data processing for industrial applications.
	\end{itemize}
}

\cventry{2022--2023}{Engineering Lead (Cybersecurity \& Cloud)}{CybelAngel}{Paris}{}{
	\begin{itemize}
		\item Led a team of 5 engineers responsible for developing internal web applications used by cybersecurity analysts to investigate and analyze data leaks.
		\item Strengthened security \& software quality through automated CI/CD, rigorous testing, and cloud-native best practices.
		\item Refactored and optimized a legacy threat detection platform, improving performance, resilience, and security posture.
	\end{itemize}
}

\cventry{2020--2022}{Engineering Lead (Cloud \& Observability)}{Datadog}{Paris}{}{
	\begin{itemize}
		\item Designed and launched the Network Device Monitoring product, leveraging cloud-based observability for large-scale IT infrastructures.
		\item Developed real-time analytics pipelines to process high-velocity telemetry data, ensuring reliable insights for enterprise customers.
		\item Mentored a team of 5 engineers in scalable cloud-native development, DevOps practices, and distributed systems design.
	\end{itemize}
}

\cventry{2013--2020}{CTO \& Co-founder (Cloud, AI \& Optimization)}{DecisionBrain}{Paris/Montpellier}{}{
	\begin{itemize}
		\item Led the company’s cloud transformation, implementing scalable SaaS architectures and AI-driven decision optimization.
		\item Designed AI-powered optimization solutions, including:
		\begin{itemize}
			\item London’s bike-sharing fleet management (predictive analytics \& optimization).
			\item Semiconductor production efficiency tools (AI-driven scheduling \& defect prevention).
			\item Hong Kong port yard optimization (real-time decision support \& logistics AI).
		\end{itemize}
		\item Scaled and managed a diverse team of 20 engineers, fostering a culture of innovation and technical excellence.
		\item Established a new office for DecisionBrain in Montpellier, expanding the company's presence and operations (15 persons).
	\end{itemize}
}

\cventry{2011--2013}{Software Architect (AI \& Data Analytics)}{Qualtera}{Montpellier}{}{
	\begin{itemize}
		\item Developed a real-time AI-powered analytics platform for the semiconductor industry, detecting anomalies with real-time machine learning models, saving clients millions in defect prevention.
	\end{itemize}
}

\cventry{2011--2013}{Software Architect \& Independent Consultant}{}{Paris}{}{
	\begin{itemize}
		\item Built a Big Data analytics platform for Mamba Nation, enabling real-time insights from large-scale user interactions.
		\item Developed \texttt{cascading.jruby}, an open-source big data processing library (now maintained by Etsy).
		\item Developed \textit{Wormee}, an online music streaming app (later integrated into Deezer).
	\end{itemize}
}

\cventry{2002--2008}{Software Architect (Enterprise AI and Rules)}{ILOG}{Paris}{}{
	\begin{itemize}
		\item Designed and developed core components of ILOG JRules, a leading Business Rules Management System (BRMS) used by Fortune 500 companies.
		\item Built the Visual Rule Editor and Business Rule Translator (BAL), enabling business users to define and modify decision rules without deep technical knowledge.
		\item Developed the Business Rules Language Definition Framework (BRLDF) and the Business Vocabulary API, allowing enterprises to customize and extend rule-based decision-making.
		\item Engineered the Visual Rule Flow Editor, an Eclipse-based modeling tool for defining and orchestrating complex business workflows.
	\end{itemize}
}

\cventry{2000--2002}{Support Engineer}{ILOG}{Paris}{}{
	\begin{itemize}
		\item Provided second-level support and consulting for ILOG JRules, ILOG Views (C++), and ILOG JViews/JTGO (Java).
		\item Assisted enterprise clients in implementing rule-based decision systems and complex visualization solutions.
		\item Authored technical documentation, FAQs, and best practices to improve developer adoption and implementation efficiency.
		\item Provided first-level support (phone and emails) for ILOG's visualization product suite (1 year).
	\end{itemize}
}


\cventry{1998--2000}{Software Developer}{Micropole}{Paris}{}{
	\begin{itemize}
		\item Developed a reservation system for Radio France, enabling secure remote access for journalists nation-wide.
	\end{itemize}
}

\section{Skills}
\cvitem{Cloud/DevOps}{Kubernetes, Docker, AWS, GCP, CI/CD, Serverless}
\cvitem{AI/ML}{Predictive Analytics, Real-time Anomaly Detection, Optimization Algorithms}
\cvitem{Data Engineering}{Big Data, Distributed Computing, Stream Processing, ETL Pipelines}
\cvitem{Cybersecurity}{Threat detection, Secure cloud architectures, Data privacy}
\cvitem{Software Architecture}{Microservices, Event-Driven Systems, Scalable SaaS Development}
\cvitem{Programming}{Python, Golang, Java, C++}


\section{Languages}
\cvitemwithcomment{French}{Native}{}
\cvitemwithcomment{English}{Fluent}{}
\cvitemwithcomment{Russian}{Basic Knowledge}{}

\section{Interests}
\cvitem{Hobbies}{Reading, Running, Photography}

\end{document}